---
title: "Simple Example: info for a gene"
author: "Charles Carey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Replicate the 11 tabs from Monarch Initiative that result from a search on a human gene.

Here are a some of them for now.

We load the monarchr client and the DT libraries. 

(DT is the datatables package which we use to display the results.)

```{r} 
library(monarchr)
library(DT)
library(knitr)
gene <- "NCBIGene:8314"
```

## Get the homologs (paralogs, orthologs and homologs) to a gene.

Homologs of gene, displayed using DataTable.

```{r homologs}
homs <- bioentity_homologs(gene)
datatable(homs$homologs)
```

## Get the diseases associated with a gene.

Diseases associated with gene, displayed using kable.

Note, the publications look clickable, but are not. This is a bug in the formatting. They are meant to be raw text.

```{r diseases}
dis <- bioentity_diseases_assoc_w_gene(gene)
kable(dis$diseases)
```

## Get the phenotypes associated with a gene.

Phenotypes associated with gene, displayed using kable.

Note, the publications look clickable, but are not. This is a bug in the formatting. They are meant to be raw text.

```{r phenotypes}
phe <- bioentity_phenotypes_assoc_w_gene(gene)
kable(head(phe$phenotypes))
```


## Get the anatomy associated with a gene.

Anatomy associated with gene, displayed using kable.

Molecularly defined by expression data?

```{r anatomy}
anat <- bioentity_exp_anatomy_assoc_w_gene(gene)
kable(head(anat$anatomy))
```

## Get the pathways associated with a gene.

Pathways associated with gene, displayed using kable.

```{r pathways}
pth <- bioentity_pathways_assoc_w_gene(gene)
kable(pth$pathways)
```

## Get the interactions associated with a gene.

Interactions associated with gene, displayed using kable.

Note, the publications look clickable, but are not. This is a bug in the formatting. They are meant to be raw text.

```{r interactions}
intx <- bioentity_interactions_assoc_w_gene(gene)
kable(head(intx$interactions))
```

<!-- Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format: -->

<!-- - Never uses retina figures -->
<!-- - Has a smaller default figure size -->
<!-- - Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style -->

<!-- ## Vignette Info -->

<!-- Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette. -->

<!-- ## Styles -->

<!-- The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows: -->

<!--     output:  -->
<!--       rmarkdown::html_vignette: -->
<!--         css: mystyles.css -->

<!-- ## Figures -->

<!-- The figure sizes have been customised so that you can easily put two images side-by-side.  -->

<!-- ```{r, fig.show='hold'} -->
<!-- plot(1:10) -->
<!-- plot(10:1) -->
<!-- ``` -->

<!-- You can enable figure captions by `fig_caption: yes` in YAML: -->

<!--     output: -->
<!--       rmarkdown::html_vignette: -->
<!--         fig_caption: yes -->

<!-- Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**. -->

<!-- ## More Examples -->

<!-- You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`. -->

<!-- ```{r, echo=FALSE, results='asis'} -->
<!-- knitr::kable(head(mtcars, 10)) -->
<!-- ``` -->

<!-- Also a quote using `>`: -->

<!-- > "He who gives up [code] safety for [code] speed deserves neither." -->
<!-- ([via](https://twitter.com/hadleywickham/status/504368538874703872)) -->
